HO unification from object language to meta language

### 2024-03-30 paper/main.tex
rework notation

When we write \Ho terms outside code blocks we follow the
usual $\lambda$-calculus notation, reserving $f, g, a, b$ for constants,
$x, y, z$ for bound variables and $X, Y, Z, F, G, H$ for unification variables.
However we need to
distinguish between the ``application'' of a unification variable
to its scope and the application of a term to a list of arguments.
We write the scope of unification variables in subscript
while we use juxtaposition for regular application.
Here a few examples:
\vspace{5pt}

\begin{tabular}{ll}
  $f~ a$ &  \elpiIn{app[con "f", con "a"]}\\
  $\lambda x.\lambda y.F_{x y}$ & \elpiIn{lam x\ lam y\ uva F [x, y]} \\
  $\lambda x.F_{x} ~ a$ & \elpiIn{lam x\ app[uva F [x], con "a"]} \\
  $\lambda x.F_{x} ~ x$ & \elpiIn{lam x\ app[uva F [x], x]} \\
\end{tabular}
\vspace{5pt}

@@

We write $\sigma = \{ A_{xy} \mapsto y\}$ for the assignment
\elpiIn{abs x\abs y\y} and $\sigma = \{ A \mapsto \lambda x.\lambda y.y\}$
for \elpiIn{lam x\lam y\y}.

>>>>

When we write \Ho terms outside code blocks we follow the
usual $\lambda$-calculus notation, reserving $f, g, a, b$ for constants,
$x, y, z$ for bound variables and $X, Y, Z, F, G, H$ for unification variables.
However we need to
distinguish between the ``application'' of a unification variable
to its scope and the application of a term to a list of arguments.
We write the scope of unification variables in subscript
while we use juxtaposition for regular application.
Here a few examples:
\vspace{4pt}

\begin{tabular}{ll}
  $f\appsep a$ &  \elpiIn{app[con "f", con "a"]}\\
  $\lambda x.\lambda y.F_{x y}$ & \elpiIn{lam x\ lam y\ uva F [x, y]} \\
  $\lambda x.F_{x} \appsep a$ & \elpiIn{lam x\ app[uva F [x], con "a"]} \\
  $\lambda x.F_{x} \appsep x$ & \elpiIn{lam x\ app[uva F [x], x]} \\
\end{tabular}
\vspace{4pt}

@@

We write $\sigma = \{~ A_{xy} \mapsto y ~\}$ for the assignment
\elpiIn{abs x\abs y\y} and $\sigma = \{~ A \mapsto \lambda x.\lambda y.y ~\}$
for \elpiIn{lam x\lam y\y}.
